Repairing cooperation through a cognitive intervention in the repeated Trust Game

### 2023-06-30 article.Rmd
Final edits

There were clear individual differences in the change of returns between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention. Some participants may not have been convinced that coaxing via high returns was a good way to establish cooperation and decided to reduce their returns in the second trust game. Their impulse to “punish” the other player for a transgression may have been too strong to be overridden by the intervention. This was also evident from the participants' replies to a question about whether they would change their behaviour, just after receiving the intervention. Other participants responded to the intervention and increased their returns. <!-- This raises important questions for the measurement of intervention effectiveness.--> Heterogeneity in response to treatment is common in psychiatry and related fields. Such heterogeneity may reflect the complex nature of mental health problems, which may be best viewed as complex systems involving interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017]. This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment response [@hitchcock_computational_2022]. <!-- MS: how do we know participants are healthy? -->As we found heterogeneity in reactions to a relatively explicit intervention by relatively healthy participants from the general population. is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself. As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.

>>>>

Analysing participants' behaviour with hidden Markov models, we found clear individual differences in how returns changed between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention. Some participants may not have been convinced that coaxing via high returns was a good way to establish cooperation and decided to reduce their returns in the second trust game. Their impulse to “punish” the other player for a transgression may have been too strong to be overridden by the intervention. This was also evident from the participants' replies to a question about whether they would change their behaviour, just after receiving the intervention. Other participants responded to the intervention and increased their returns. <!-- This raises important questions for the measurement of intervention effectiveness.--> Heterogeneity in response to treatment is common in psychiatry and related fields. Such heterogeneity may reflect the complex nature of mental health problems, which may be best viewed as complex systems involving interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017]. This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment response [@hitchcock_computational_2022]. <!-- MS: how do we know participants are healthy? -->As we found heterogeneity in reactions to a relatively explicit intervention by relatively healthy participants from the general population. is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself. As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.
